Spatial Coordination Of Stomatal Patterning Between Leaf Surfaces In Amphistomatous \emph{Arabidopsis thaliana} Incurs No Photosynthetic Advantage

### 2023-10-17 ms/ms.Rmd
added stomatal density results to ms

```{r}
source("r/header.R")
fit = readr::read_rds("objects/fit.rds")
single_surface_results = readr::read_rds("objects/single_surface_results.rds")
single_surface_anova = readr::read_rds("objects/single_surface_anova.rds")
pm_pars = readr::read_csv("raw-data/2d-pm-parameters.csv", show_col_types = FALSE)
model_var = readr::read_rds("objects/model_var.rds")

@@

Stomatal density of *Arabidopsis thaliana* the `r nrow(single_surface_results)` leaf surfaces measured ranged from 12 to 93 (units) with high light leaves ranging from 93 to 55 (units), medium light from 15 to 35 (units), and low light from 12 to 42 (units). Leaves were amphistomatous with a mean stomatal ratio of 0.45.

@@

Rather than regulate stomatal patterning in response to light regimes, plants respond by increasing stomatal density (\autoref{fig:density}). Stomatal density drastically increased in plants grown under high light, validating the long held hypothesis that light strongly influences stomatal density (F$_\text{2,126}$ = 680.7; p-value < 0.001).

Across all light treatments and leaf surfaces, stomatal length and stomatal area were weakly positively correlated, indicating some support for our hypothesis that stomata are selected for an optimal operational aperture (\autoref{fig:length-area}).

>>>>

```{r}
source("r/header.R")
fit = readr::read_rds("objects/fit.rds")
single_surface_results = readr::read_rds("objects/single_surface_results.rds")
single_surface_anova = readr::read_rds("objects/single_surface_anova.rds")
density_anova = readr::read_rds("objects/density_anova.rds")
pm_pars = readr::read_csv("raw-data/2d-pm-parameters.csv", show_col_types = FALSE)
model_var = readr::read_rds("objects/model_var.rds")

@@

Stomatal density of *Arabidopsis thaliana* the `r nrow(single_surface_results)` leaf surfaces measured range from 12 to 93 (units) with high light leaves ranging from 93 to 55 (units), medium light from 15 to 35 (units), and low light from 12 to 42 (units). Stomatal density varies among light treatments (ANOVA, $`r report_fstat(density_anova, 'light')`$) because the density is much greater in the high light treatment (\autoref{fig:density}). Density is consistently greater on abaxial leaf surfaces across all light treatments (ANOVA, $`r report_fstat(density_anova, 'surface')`$; \autoref{fig:density}). There is no evidence for an interaction between light treatment and surface (ANOVA, $`r report_fstat(density_anova, 'light:surface')`$). Leaves are amphistomatous with a mean stomatal density ratio of 0.45.

@@

<!-- WORKING HERE -->
Across all light treatments and leaf surfaces, stomatal length and stomatal area were weakly positively correlated, indicating some support for our hypothesis that stomata are selected for an optimal operational aperture (\autoref{fig:length-area}).

### 2023-10-17 ms/ms.tex
added stomatal density results to ms

Stomatal density of \emph{Arabidopsis thaliana} the 132 leaf surfaces
measured ranged from 12 to 93 (units) with high light leaves ranging
from 93 to 55 (units), medium light from 15 to 35 (units), and low light
from 12 to 42 (units). Leaves were amphistomatous with a mean stomatal
ratio of 0.45.

@@

Rather than regulate stomatal patterning in response to light regimes,
plants respond by increasing stomatal density (\autoref{fig:density}).
Stomatal density drastically increased in plants grown under high light,
validating the long held hypothesis that light strongly influences
stomatal density (F\(_\text{2,126}\) = 680.7; p-value \textless{}
0.001).

>>>>

Stomatal density of \emph{Arabidopsis thaliana} the 132 leaf surfaces
measured range from 12 to 93 (units) with high light leaves ranging from
93 to 55 (units), medium light from 15 to 35 (units), and low light from
12 to 42 (units). Stomatal density varies among light treatments (ANOVA,
\(F_{2,126} = 681, P = 2.88 \times 10^{-68}\)) because the density is
much greater in the high light treatment (\autoref{fig:density}).
Density is consistently greater on abaxial leaf surfaces across all
light treatments (ANOVA, \(F_{1,126} = 44.2, P = 8.21 \times 10^{-10}\);
\autoref{fig:density}). There is no evidence for an interaction between
light treatment and surface (ANOVA,
\(F_{2,126} = 2.75 \times 10^{-2}, P = 0.973\)). Leaves are
amphistomatous with a mean stomatal density ratio of 0.45.

@@
